---
title: "Biostat 200B Project"
subtitle: NINDS datase
author: Xin Xie, Xingjian Xie, Yue Wang, Zoe Zhao
format:
  html:
    theme: cosmo
    number-sections: true
    toc: true
    toc-depth: 4
    toc-location: left
    code-fold: false
knitr:
  opts_chunk: 
    cache: false    
    echo: true
    fig.align: 'center'
    fig.width: 6
    fig.height: 4
    message: FALSE
---


```{r}
library(dplyr)
require(haven)
library(ggplot2)
library(psych)
library(performance)
library(caret)
library(corrplot)
library(gridExtra)
library(olsrr)
```


**read the data files**

```{r}
# NINDS = read_sas('originalninds.sas7bdat')
NINDS<-read_sas("/Users/Aoki/Desktop/UCLA/Quarter_2/BIOSTATS_200B/Winter_BIO200B_Group8/originalninds.sas7bdat")
```


```{r}
names(NINDS)
```


## 1. Dataset Preparation

**Select the variables**
Predictor variables (tentative list) 
X1: nihssb (nih stroke scale at baseline)
X2: age (age in years)
X3: brace (patient's race)
X4: bgender (patient's gender)
X5: bhyper (history of hypertension at baseline)
X6: bdiab (history of diabetes at baseline)
X7: cursmker (smoking (in year) prior to this stroke)


We new add some more variables into the model. 
Add hour24 treatcd ninety



```{r}
NINDS <- NINDS %>%
select(,los,nihssb,age,brace,bgender,bhyper,bdiab,cursmker,hour24,treatcd,ninety,int3mles,oldvol)
```

**delet NA variabls and plot the summary of the variables**

```{r}
NINDS <- na.omit(NINDS)
summary(NINDS)
```

**create dummy variables**

**Reference :**
#male=0, no hypertention history, no diabeties history, no smoke history, white people. 


```{r}
NINDS <- NINDS %>%
  

mutate(gender = ifelse(NINDS$bgender == 1, 1, 0),
       hypertension1 = ifelse(NINDS$bdiab == 100, 1, 0),
       diabetes1 = ifelse(NINDS$bdiab == 100, 1, 0),
       smoke1 = ifelse(NINDS$bdiab == 100, 1, 0),
       black = ifelse(NINDS$brace == 1, 1, 0),
       hispanic = ifelse(NINDS$brace == 3, 1, 0),
       asian = ifelse(NINDS$brace == 4, 1, 0),
       other = ifelse(NINDS$brace == 5, 1, 0),
       prtreat = ifelse(NINDS$treatcd == 1, 1, 0),
       # heparin =ifelse(NINDS$heparin == 1, 1, 0),
       # preccb =ifelse(NINDS$preccb == 1, 1, 0),
       )

# NINDS$ninety [NINDS$ninety == 42 ] <- NA
# NINDS$hour24 [NINDS$hour24 == 42] <- NA

# select(,nihssb,age,brace,male,female,hypertension,diabetes,smoke) 
NINDS 

#write.csv(NINDS,"/Users/Aoki/Desktop/UCLA/Quarter_2/BIOSTATS_200B/Winter_BIO200B_Group8/NINDS.csv")
```



## 2. Plots for our variabls
```{r}
NINDS = NINDS %>%
select(c('gender','hypertension1','diabetes1','smoke1','black','hispanic',
         'asian', 'other', 'los', 'nihssb', 'age','hour24','treatcd', 'ninety', 'int3mles','oldvol'))
NINDS$los=log(NINDS$los)
NINDS$hour24=log(NINDS$hour24)
NINDS$int3mles=log(NINDS$int3mles)
NINDS$los[!is.finite(NINDS$los)] = NA
NINDS$hour24[!is.finite(NINDS$hour24)] = NA
NINDS$int3mles[!is.finite(NINDS$int3mles)] = NA
NINDS$oldvol[!is.finite(NINDS$oldvol)] = NA
NINDS <- na.omit(NINDS)

```

```{r}
write.csv(NINDS,"/Users/Aoki/Desktop/UCLA/Quarter_2/BIOSTATS_200B/Winter_BIO200B_Group8/NINDS.csv")

names(NINDS)
NINDS %>%
pairs.panels()

NINDS %>%
ggplot() + 
geom_point(mapping = aes(x = oldvol , y = hour24))

NINDS %>% 
ggplot(,mapping = aes(x = oldvol)) + 
  geom_boxplot()

```




```{r}
model = lm(los~gender + hypertension1 + black + hispanic + asian + other + nihssb +
     age +treatcd +ninety +int3mles,
     data = NINDS)

model1 = lm (hour24~ treatcd + nihssb + ninety +  oldvol , data = NINDS)
```

```{R}

model %>%
  summary()

model1 %>%
  summary()
```

```{r}

NINDS1 <- NINDS %>%
  select(hour24, treatcd , nihssb , ninety , int3mles,oldvol)
  
plot1<-cor(x = NINDS1, use = "pairwise")
plot1
corrplot(plot1, method = "circle", order= "hclust")
```

```{r}
qqnorm(NINDS$hour24)
qqline(NINDS$hour24)
```

```{r}
abc<- abc %>%
  select('24hour_scale', Lesion_volume, Gender, Baseline_scale, Black, Hispanic, Asian,
         Other_race, age, Treatment, Length_of_Stay, Hypertension, '7to10days_Scale') %>%
  rename(  Age=age)

plot2<-cor(x = abc, use = "pairwise")
plot2
corrplot(plot2, method = "ellipse", order= "AOE", type = "upper")
```



