---
title: "Biostat 200B Project"
subtitle: NINDS datase
author: Xin Xie, Xingjian Xie, Yue Wang, Zoe Zhao
format:
  html:
    theme: cosmo
    number-sections: true
    toc: true
    toc-depth: 4
    toc-location: left
    code-fold: false
knitr:
  opts_chunk: 
    cache: false    
    echo: true
    fig.align: 'center'
    fig.width: 6
    fig.height: 4
    message: FALSE
---


```{r}
library(dplyr)
require(haven)
library(ggplot2)
library(psych)
library(performance)
```


**read the data files**

```{r}
NINDS = read_sas('originalninds.sas7bdat')
#NINDS<-read_sas("/Users/Aoki/Desktop/UCLA/Quarter_2/BIOSTATS_200B/Winter_BIO200B_Group8/originalninds.sas7bdat")
```


## 1. Dataset Preparation

**Select the variables**
Predictor variables (tentative list) 
X1: nihssb (nih stroke scale at baseline)
X2: age (age in years)
X3: brace (patient's race)
X4: bgender (patient's gender)
X5: bhyper (history of hypertension at baseline)
X6: bdiab (history of diabetes at baseline)
X7: cursmker (smoking (in year) prior to this stroke)


```{r}
NINDS <- NINDS %>%
select(,los,nihssb,age,brace,bgender,bhyper,bdiab,cursmker)
```

**delet NA variabls and plot the summary of the variables**

```{r}
NINDS <- na.omit(NINDS)
summary(NINDS)
```

**create dummy variables**

**Reference :**
#female, no hypertention history, no diabeties history, no smoke history. 


```{r}
NINDS <- NINDS %>%
  
 # NINDS$gender <- ifelse(NINDS$bgender == 1, 1, 0)

mutate(gender = ifelse(NINDS$bgender == 1, 1, 0),
       hypertension1 = ifelse(NINDS$bdiab == 100, 1, 0),
       diabetes1 = ifelse(NINDS$bdiab == 100, 1, 0),
       smoke1 = ifelse(NINDS$bdiab == 100, 1, 0),
       black = ifelse(NINDS$brace == 1, 1, 0),
       hispanic = ifelse(NINDS$brace == 3, 1, 0),
       asian = ifelse(NINDS$brace == 4, 1, 0),
       other = ifelse(NINDS$brace == 5, 1, 0),
       )
# select(,nihssb,age,brace,male,female,hypertension,diabetes,smoke) 
NINDS 

#write.csv(NINDS,"/Users/Aoki/Desktop/UCLA/Quarter_2/BIOSTATS_200B/Winter_BIO200B_Group8/NINDS.csv")
```



## 2. Plots for our variabls
```{r}
NINDS = NINDS %>%
select(c('gender','hypertension1','diabetes1','smoke1','black','hispanic',
         'asian', 'other', 'los', 'nihssb', 'age'))
NINDS$los=log(NINDS$los)
NINDS$los[!is.finite(NINDS$los)] = NA
remove_missing(NINDS)

NINDS %>%
  ggplot(aes(y = los, x = nihssb, color = gender)) + geom_point() +
  geom_smooth()
```

```{r}
NINDS %>%
pairs.panels()
```




```{r}
model = lm(los~gender + hypertension1 + black + hispanic + asian + other + nihssb + 
     age,
   data = NINDS)
model %>%
  check_collinearity()
```

```{R}
model %>%
  summary()
```

