---
title: "Biostat 200B Project"
subtitle: NINDS datase
author: Xin Xie, Xingjian Xie, Yue Wang, Zoe Zhao
format:
  html:
    theme: cosmo
    number-sections: true
    toc: true
    toc-depth: 4
    toc-location: left
    code-fold: false
knitr:
  opts_chunk: 
    cache: false    
    echo: true
    fig.align: 'center'
    fig.width: 6
    fig.height: 4
    message: FALSE
---


```{r}
library(dplyr)
require(haven)
```


**read the data files**

```{r}
NINDS<-read_sas("/Users/Aoki/Desktop/UCLA/Quarter_2/BIOSTATS_200B/Winter_BIO200B_Group8/originalninds.sas7bdat")
```


## 1. Dataset Preparation

**Select the variables**
Predictor variables (tentative list) 
X1: nihssb (nih stroke scale at baseline)
X2: age (age in years)
X3: brace (patient's race)
X4: bgender (patient's gender)
X5: bhyper (history of hypertension at baseline)
X6: bdiab (history of diabetes at baseline)
X7: cursmker (smoking (in year) prior to this stroke)


```{r}
NINDS <- NINDS %>%
select(,los,nihssb,age,brace,bgender,bhyper,bdiab,cursmker)
```

**delet NA variabls and plot the summary of the variables**

```{r}
NINDS <- na.omit(NINDS)
summary(NINDS)
```

**create dummy variables**

**Reference :**
#male=0, no hypertention history, no diabeties history, no smoke history, white people. 


```{r}
NINDS <- NINDS %>%
  
 # NINDS$gender <- ifelse(NINDS$bgender == 1, 1, 0)

mutate(gender = ifelse(NINDS$bgender == 1, 1, 0),
       hypertension1 = ifelse(NINDS$bdiab == 100, 1, 0),
       diabetes1 = ifelse(NINDS$bdiab == 100, 1, 0),
       smoke1 = ifelse(NINDS$bdiab == 100, 1, 0),
       black = ifelse(NINDS$brace == 1, 1, 0),
       hispanic = ifelse(NINDS$brace == 3, 1, 0),
       asian = ifelse(NINDS$brace == 4, 1, 0),
       other = ifelse(NINDS$brace == 5, 1, 0),
       )
# select(,nihssb,age,brace,male,female,hypertension,diabetes,smoke) 
NINDS 

write_sas(NINDS, "/Users/Aoki/Desktop/UCLA/Quarter_2/BIOSTATS_200B/Winter_BIO200B_Group8/NINDS.sas7bdat")
```



## 2. Plots for our variabls

```{r}
write.csv(NINDS,"/Users/Aoki/Desktop/UCLA/Quarter_2/BIOSTATS_200B/Winter_BIO200B_Group8/NINDS.csv")

names(NINDS)
```


